Variable Circular Plots: Station Placement and the Independence Assumption

### 2014-06-09 presentation/VCPSlides.tex
FInal Slides update for tonight
modified a copule graphics to fit presentation color scheme.
updated slides and notes.

\mode<presentation>
{
	\usetheme{CambridgeUS}
	\setbeamercovered{transparent}
	\setbeamertemplate{footline}[page number]{}
	\setbeamertemplate{navigation symbols}{} % remove navigation symbols
	\setbeamercolor{palette tertiary}{fg=white, bg=OSUdkbrn}
	\setbeamercolor{title}{fg=OSUdkbrn}
	\setbeamercolor{frametitle}{fg=OSUdkbrn}
	\setbeamertemplate{itemize items}[square]
	\setbeamercolor*{item}{fg=OSUdkbrn}
%	
%	\setbeameroption{show only notes} % ----------------------- NOTES TOGGLE ---------------------
%
}

@@

\begin{frame}{VCP Indepencence}
	\begin{itemize}
	\item \textcite{ramsey1979,buckland1987,thompson2012} discuss assumption that VCPs are randomly placed.
	\begin{itemize}
	\item Implicit, but not explicit, possibility of overlap
	\end{itemize}
	\item[]
	\item \textcite{reynolds1980} state the possibility of observing the same bird from more than one station should be avoided.
	\item[]
	\item \textcite{buckland2001} states ``Transects are normally spaced at a sufficient distance to avoid detecting an object from two neighboring transacts, although this is not usually critical unless sampling a line changes the animal distribution at neighboring, as yet un-sampled lines.''
	\end{itemize}

@@

\begin{frame}{Transect Layouts}
1 unit on graph = 1000 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT2.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT1.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Structured and Random Layouts}
1 unit on graph = 1000 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutS.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutR.pdf}
		\end{column}
	\end{columns}

@@

	\begin{columns}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutS.pdf}
		\end{column}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutR.pdf}
		\end{column}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT2.pdf}
		\end{column}
	\end{columns}
	\vspace{1cm}
	1 unit = 1000 km, circles represent 200 m out from station
	\note{
		\begin{itemize}
		\item Makes sense for structured, if the objects are only moving within the first 100 m, they would not move twice.
		\item For the Randomized Layout, there are only 3, in this example, where there is a significant amount of overlap. If we take this as representative of the population of layouts, we would not be seeing many layouts with a significant amount of double or triple movement. An estimate from this layout should be similar to the Structured Layout, which we see.
		\item It's with the Transect layout where the most compounded movement occurs.
		\item (Go Back 1 Slide) There may be an effect of the combination of The Compounded movement and the Transect layout.
		\item not sure if this is bias reduction, or an upward bias that looks like bias reduction because we're already low.
		\end{itemize}
	}
\end{frame}

% -------------------------------- Lines vs. Circles --------------------------------------------------
\section{Problem with Circles}

>>>>

\mode<presentation>
{
	\usetheme{CambridgeUS}
	\setbeamercovered{transparent}
	\setbeamertemplate{footline}[page number]{}
	\setbeamertemplate{navigation symbols}{} % remove navigation symbols
	\setbeamercolor{palette tertiary}{fg=white, bg=OSUdkbrn}
	\setbeamercolor{title}{fg=OSUdkbrn}
	\setbeamercolor{frametitle}{fg=OSUdkbrn}
	\setbeamertemplate{itemize items}[square]
	\setbeamercolor*{item}{fg=OSUdkbrn}
%	
	\setbeameroption{show only notes} % ----------------------- NOTES TOGGLE ---------------------
%
}

@@

\begin{frame}{VCP Indepencence}
	\begin{itemize}
	\item \textcite{ramsey1979,buckland1987,thompson2012} discuss assumption that VCPs are randomly placed.
	\begin{itemize}
	\item Implicit, but not explicit, possibility of overlap
	\end{itemize}
	\item[]
	\item \textcite{reynolds1980} state the possibility of observing the same bird from more than one station should be avoided.
	\item[]
	\item \textcite{buckland2001} states ``Transects are normally spaced at a sufficient distance to avoid detecting an object from two neighboring transects, although this is not usually critical unless sampling a line changes the animal distribution at neighboring, as yet un-sampled lines.''
	\end{itemize}

@@

\begin{frame}{Transect Layouts}
1 unit on graph = 1 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT2.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT1.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Structured and Random Layouts}
1 unit on graph = 1 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutS.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutR.pdf}
		\end{column}
	\end{columns}

@@

	\begin{columns}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutS.pdf}
		\end{column}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutR.pdf}
		\end{column}
		\begin{column}{0.3\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT2.pdf}
		\end{column}
	\end{columns}
	\vspace{1cm}
	1 unit = 1 km, circles represent 200 m out from station
	\note{
		\begin{itemize}
		\item Makes sense for structured, if the objects are only moving within the first 100 m, they would not move twice.
		\item For the Randomized Layout, there are only 3, in this example, where there is a significant amount of overlap. If we take this as representative of the population of layouts, we would not be seeing many layouts with a significant amount of double or triple movement. An estimate from this layout should be similar to the Structured Layout, which we see.
		\item It's with the Transect layout where the most compounded movement occurs.
		\item (Go Back 1 Slide) There may be an effect of the combination of The Compounded movement and the Transect layout.
		\item not sure if this is bias reduction, or an upward bias that looks like bias reduction because we're already low.
		\end{itemize}
	}
\end{frame}

% -------------------------------- Lines vs. Circles --------------------------------------------------
\section{Problems}

\begin{frame}{Movement Testing}
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../images/movementTest.pdf}
	\end{figure}
\end{frame}

\begin{frame}{Change in Area}

	\begin{columns}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/slides-LTr.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/slides-VCPr.pdf}
		\end{column}
	\end{columns}

\begin{frame}{Circles vs. Rectangles}{Area and Expected Observation Counts}
	\begin{columns}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/rect-circ-area.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/rect-circ-detection.pdf}
		\end{column}
	\end{columns}
	\begin{center}
	\par Solid line is Line Transect, Dashed line is VCP
	\end{center}
